### 2018-08-06 paper/design.tex

\sonja{Here comes more of a solution overview and reference to the outline
  figure.}
Figure \cref{fig:outline} shows the components needed to obtain this
routing information.

>>>>

\sonja{Here comes more of a solution overview and reference to the outline
  figure.}
Figure~\ref{fig:outline} shows the components needed to obtain this
routing information.
